---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)
```

# odsrmd

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub](https://img.shields.io/github/license/opendatasoft/odsrmd?style=plastic)
![GitHub R package version](https://img.shields.io/github/r-package/v/opendatasoft/odsrmd?style=plastic)
<!-- badges: end -->

The goal of {odsrmd} is to give the possibility to R users to add Rmarkdown files as pages on an Opendatasoft platform. It knits an Rmarkdown file to html, format it to JSON and send it via the management API on an Opendatasoft platform.    
Note that you cannot include scripts on a classic page from the Opendatasoft platform. Interactive libraries such as {plotly} or {highcharter} produce script nodes when the document is knitted to html. Hence they cannot be used in Rmarkdown documents that you intend to display as a page on an Opendatasoft platform. For the same reasons, {bookdown} and {flexdashboard} are not compatible with {odsrmd}.             
    

## Installation

You can install the development version of odsrmd like so:

``` r
# remotes::install_github("odsrmd")
```


## Authentication   

To use this package, you must be granted credentials to access an Opendatasoft platform. These credentials should be stored in your .Renviron file. 

Open the .Renviron file:     
```{r, eval=FALSE}
usethis::edit_r_environ()
```

Add the following environment variables: `ODS_DOMAIN_ID`, `ODS_USERNAME` and `ODS_PASSWORD`. The `ODS_DOMAIN_ID` variable corresponds to the domain ID of your Opendatasoft domain. `ODS_USERNAME` and `ODS_PASSWORD` correspond respectively to your username and password to access the platform.      
Be very careful to not display such information in a script and add the .Renviron file to your .gitignore file. 

```{r}
usethis::use_git_ignore(ignores = ".Renviron")
```



## Example

Here is a minimal example on how to use the {odsrmd} package.

First, login on your Opendatasoft platform, go to the backoffice, create a classic page and write "test" as the page URL. Then, add your credentials and domain ID to the .Renviron file. 
Now run the example below. 

```{r example, eval=FALSE}
library(odsrmd)

# Create a temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

# Use example Rmd from the {odsrmd} library
file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to=dir_tmp)
file.copy(from = system.file("examples/style.css", package = "odsrmd"), to=dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")

# Here the page to modify on the Opendatasoft platform is named "test"   
page_slug <- "test"

# Send elements to the page on the Opendatasoft platform
update_ods_page(path, page_slug, add_extra_css = "no", chosen_languages = "all", title = NULL,
  description = NULL, tags = NULL, restricted = NULL
)

```

## Getting help 

First, we suggest to try some general troubleshooting strategies:      
- Check that you added your credentials to the .Renviron file. Check that you use a plain Rmarkdown file (no {flexdashboard}, no {pagedown}).        
- Try to find out what the specific problem is, notably by identifying what is *not* causing the problem.          
- “Unplug and plug it back in”: restart R, close and reopen R.              

You can also submit an issue on Github if your question is directly related to the package {odsrmd}. Please indicate your version of R and of {odsrmd}, and provide a minimal version of the Rmarkdown document you would like to publish as a page on your platform.       

Your question concerns your platform, your credentials etc? Please contact the Opendatasoft support or get in touch with your Customer Success Manager.            

## Code of Conduct

Please note that the {odsrmd} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.





