---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# odsrmd

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of odsrmd is to give the possibility to R users to add Rmarkdown files as pages on an Opendatasoft platform. It knits an Rmarkdown file to html, format it to JSON and send it via the management API on an Opendatasoft platform.    

## Installation

You can install the development version of odsrmd like so:

``` r
# remotes::install_github("odsrmd")
```


## Authentication   

To use this package, you must be granted credentials to access an Opendatasoft platform. These credentials should be stored in your .Renviron file. 

Open the .Renviron file:     
```{r, eval=FALSE}
usethis::edit_r_environ()
```

Add the following environment variables: `ODS_DOMAIN_ID`, `ODS_USERNAME` and `ODS_PASSWORD`. The `ODS_DOMAIN_ID` variable corresponds to the domain ID of your Opendatasoft domain. `ODS_USERNAME` and `ODS_PASSWORD` correspond respectively to your username and password to access the platform.      
Be very careful to not display such information in a script and add the .Renviron file to your .gitignore file. 

```{r}
usethis::use_git_ignore(ignores = ".Renviron")
```



## Example

Here is a minimal example on how to use the {odsrmd} package.

First, login on your Opendatasoft platform, go to the backoffice and create a classic page and write "test" as the page URL. Then, add your credentials and domain ID to the .Renviron file. 
Now run the example below. 

```{r example, eval=FALSE}
library(odsrmd)

# Create a temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

# Use example Rmd from the {odsrmd} library
file.copy(from = system.file("data/example_rmd.Rmd", package = "odsrmd"), to=dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")

# Here the page to modify on the Opendatasoft platform is named "test"   
page_slug <- "test"

# Knit the Rmarkdown file
body_and_style <- get_body_and_style(path)

# Get elements from the page on the Opendatasoft platform
page_elements <- get_ods_page(page_slug)

# Prepare elements to send on the page on the Opendatasoft platform
json_to_send <- create_json(page_elements, body_and_style, language = NULL, 
                        title = NULL, description = NULL, template = NULL, 
                        tags = NULL, restricted = NULL)

# Send elements to the page on the Opendatasoft platform
put_ods_page(page_slug, json_to_send)

```

## Code of Conduct

Please note that the odsrmd project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.





