---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  results = FALSE
)
```


```{r development, include=FALSE}
library(testthat)
library(rmarkdown)

library(rvest)
library(glue)
library(httr2)
library(jsonlite)
library(purrr)

# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)
```

```{r, message=FALSE}
library(dplyr)
```

This vignette guides you through the procedure to display the content of an Rmarkdown file on a classic page from the Opendatasoft platform. Here we will take a simple Rmarkdown file, stored as example in the package {odsrmd}. You can prepare you own Rmarkdown file. Note that you can query data from your own platform using the [API version 2](https://help.opendatasoft.com/apis/ods-explore-v2/). 


We assume that you have access to an Opendatasoft platform and have the rights to create and edit a page on the platform. As described in the README, you need to add the following environment variables to your Renviron file: `ODS_DOMAIN_ID`, `ODS_USERNAME` and `ODS_PASSWORD`. The `ODS_DOMAIN_ID` variable corresponds to the domain ID of your Opendatasoft domain. `ODS_USERNAME` and `ODS_PASSWORD` correspond respectively to your username and password to access the platform.        
We also assume that you already created an empty classic page, for which the page URL (or page slug) is "test".




<!-- ## api_error_body -->

    
```{r function-api_error_body}
#' Extract error messages and warnings sent by the API
#'
#' @param resp A response object. 
#'
#' @return The message and error parts from the content-type header. 
#' @importFrom httr2 resp_body_json
#' @importFrom purrr map_chr pluck
#' @noRd
api_error_body <- function(resp) {
  resp_tmp <- resp %>%
    resp_body_json() 
  
  if (!is.null(resp_tmp$message)){
    message <- resp_tmp$message
  }else{
    message <- ""
  }
  
  if (!is.null(resp_tmp$error)){
    error <- resp_tmp$error
  }else{
    error <- ""
  }
  
  if (!is.null(resp_tmp$errors)){
    
    detailed_errors <- map_chr(length(resp_tmp$errors), function(x){
      error_keys <- pluck(resp_tmp, "errors", 1, "error_key")
      error_messages <- pluck(resp_tmp, "errors", 1, "message")
      paste(error_keys, error_messages, sep = "\n")
    }
    )
  }else{
    detailed_errors <- ""
  }
  
  message(paste(error, message, detailed_errors, sep = "\n"))
}
```
  
```{r example-api_error_body, eval=FALSE, echo=FALSE}
#' \dontrun{
#' library(httr2)
#' 
#' ods_domain_id <- Sys.getenv("ODS_DOMAIN_ID")
#' ods_username <- Sys.getenv("ODS_USERNAME")
#' ods_password <- Sys.getenv("ODS_PASSWORD")
#' 
#' domain_url <- paste0("https://", ods_domain_id, ".opendatasoft.com/api/management/v2/")
#' page_slug <- "testthat-odsrmd"
#' 
#' resp <- request(domain_url) %>%
#'   req_auth_basic(username = ods_username, password = ods_password) %>%
#'   req_url_path_append("p", page_slug) %>%
#'   req_user_agent("R package odsrmd") %>%
#'   req_perform()
#' 
#' api_error_body(last_response())
#' }
```
  
```{r tests-api_error_body}
test_that("api_error_body works", {
  expect_true(inherits(api_error_body, "function")) 
})
```
  






    
## get_body_and_style
    
Here we render the Rmarkdown file as an .html file and extract the html the html nodes corresponding to body and style of the page. You cannot include scripts on a classic page from the Opendatasoft platform. Scripts nodes are removed from the html document and interactive libraries such as {plotly} or {highcharter} cannot be used here in the Rmarkdown document.     
    
```{r function-get_body_and_style}
#' Get body and style
#' 
#' Render Rmarkdown file as html file and extract the html nodes corresponding to body and style without the script nodes.    
#' 
#' @param path Path to the Rmd file. 
#'
#' @return A named list with two elements : body and style. 
#' @importFrom rmarkdown render
#' @importFrom rvest read_html html_elements html_text html_nodes
#' @importFrom glue glue_collapse
#' @importFrom magrittr %>%
#' 
#' @export 
get_body_and_style <- function(path) {
  render(path, output_format = "html_document", output_options = "self-contained", 
         envir = new.env(), quiet = TRUE)

  path_html <- gsub(pattern = ("[.]rmd|[.]Rmd"), replacement = ".html", x = path)

  html_content <- read_html(path_html)
  style <- html_elements(html_content, "style") %>%
    html_text() %>%
    glue_collapse()

  body <- html_elements(html_content, "body>:not(script)") %>%
    glue_collapse()

  list(body = body, style = style)
}
```
  
```{r example-get_body_and_style}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to=dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")

body_and_style <- get_body_and_style(path)
```
  
```{r tests-get_body_and_style}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to=dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")

output <- get_body_and_style(path)

test_that("get_body_and_style works", {
  expect_true(inherits(get_body_and_style, "function"))
  expect_type(output, "list")
  expect_length(output, 2)
  expect_identical(names(output), c("body", "style"))
})
```



## get_ods_page
    
Here we assume that you have access to an Opendatasoft platform and have the rights to create and edit a page on the platform. We also assume that you added the `ODS_DOMAIN_ID`, `ODS_USERNAME` and `ODS_PASSWORD`environment variables to your Renviron file.   
And we also assume that you already created an empty classic page on the platform, for which the page URL (or page slug) is "test".     

The get_ods_page() function gets all pre-existing information of the page, such as its title, description, tags and current content. If no other information is provided, these elements will be re-used in create_json() to create the JSON object that will be sent back on the Opendatasoft platform using the put_ods_page() function.       

```{r function-get_ods_page}
#' Get ODS page
#' 
#' Get the content of a classic page from an Opendatasoft platform.   
#' 
#' @param page_slug Slug of the page (in the backoffice of the platform -> Pages -> New or existing page -> Properties -> Page URL). 
#'
#' @return A list object containing the information from the page (title, description, tags...). 
#' @importFrom httr2 request req_auth_basic req_url_path_append req_user_agent req_error req_perform resp_body_json
#' 
#' @export
get_ods_page <- function(page_slug) {
  if (page_slug == "") {
    stop(
      "Please provide a unique page slug\n",
      'With "", you are trying to query all pages at the same time!'
    )
  }

  ods_domain_id <- Sys.getenv("ODS_DOMAIN_ID")
  ods_username <- Sys.getenv("ODS_USERNAME")
  ods_password <- Sys.getenv("ODS_PASSWORD")

  if (ods_domain_id == "") {
    stop(
      "The domain identifier of the Opendatasoft platform is missing.\n",
      "Please add the environmental variable ODS_DOMAIN_ID to your .Renviron file with the corresponding domain identifier.\n",
      "Reminder, your domain identifier is part of your domain URL : https://your_domain_ID.opendatasoft.com/"
    )
  }

  if (ods_username == "") {
    stop(
      "Your username is missing.\n",
      "Please add the environmental variable ODS_USERNAME to your .Renviron file with the corresponding username.\n"
    )
  }

  if (ods_password == "") {
    stop(
      "Your password is missing.\n",
      "Please add the environmental variable ODS_PASSWORD to your .Renviron file with the corresponding password\n"
    )
  }

  domain_url <- paste0("https://", ods_domain_id, ".opendatasoft.com/api/management/v2/")

  resp <- request(domain_url) %>%
    req_auth_basic(username = ods_username, password = ods_password) %>%
    req_url_path_append("pages", page_slug) %>%
    req_user_agent("R package odsrmd") %>%
    req_error(body = api_error_body) %>%
    req_perform()

  resp %>% resp_body_json()
}

```
  
```{r example-get_ods_page}
page_slug <- "testthat-odsrmd" 
page_elements <- get_ods_page(page_slug) 

```
  
```{r tests-get_ods_page}
page_slug <- "testthat-odsrmd"
page_elements <- get_ods_page(page_slug)

test_that("get_ods_page works", {
  expect_true(inherits(get_ods_page, "function"))
  expect_type(page_elements, "list")
  expect_length(page_elements, 13)
  expect_error(get_ods_page(page_slug = ""))
  expect_identical(names(page_elements), c("slug", "title", "description", "template", "content",
                                           "tags", "restricted", "pushed_by_parent", 
                                           "has_subdomain_copies", "created_at", "last_modified",
                                           "last_modified_user", "author"))
  expect_type(page_elements$title, "list")
  expect_type(page_elements$content, "list")
  expect_type(page_elements$tags, "list")
  expect_type(page_elements$last_modified_user, "list")
  expect_type(page_elements$author, "list")
})

```
  
## get_languages
    
```{r function-get_languages}
#' Get all languages available on the ODS platform
#' 
#' Retrieve all languages available on the ODS platform from the information contained in page_elements.
#' 
#' @param page_elements List object from get_page(). Contains the title, description, template, language, content, tags and level of restriction of the page. 
#' @param verbose A logical TRUE/FALSE indicating if the function should output a message listing the languages available on the platform.   
#'
#' @return A vector of characters. 
#' @importFrom glue glue_collapse glue
#' 
#' @export
get_languages <- function(page_elements, verbose = TRUE) {
  all_languages <- names(page_elements$content$html)
  all_languages_list <- glue_collapse(all_languages, sep = ", ") %>% toupper()

  if (verbose) {
    message(glue("Languages available on the platform: {all_languages_list}."))
  }

  all_languages
}
```
  
```{r example-get_languages}
page_slug <- "testthat-odsrmd"
page_elements <- get_ods_page(page_slug) 

all_languages <- get_languages(page_elements)
```
  
```{r tests-get_languages}
page_slug <- "testthat-odsrmd"
page_elements <- get_ods_page(page_slug)

all_languages <- get_languages(page_elements)

test_that("get_languages works", {
  expect_true(inherits(get_languages, "function"))
  expect_type(all_languages, "character")
  expect_message(get_languages(page_elements))
  expect_silent(get_languages(page_elements, verbose = FALSE))
})
```
  

## is_available
    
```{r function-is_available}
#' Check language availability
#' 
#' Check if a given language is available on the ODS platform from the list of languages contained in page_elements. 
#' 
#' @param language Character string. 
#' @param page_elements List object from get_page(). Contains the title, description, template, language, content, tags and level of restriction of the page. 
#'
#' @importFrom glue glue
#' 
#' @export
is_available <- function(language, page_elements) {
  if (!tolower(language) %in% get_languages(page_elements, verbose = FALSE)) {
    stop(
      glue("Language '{language}' is not available on the platform. To add more languages to your platform, please contact your administrator or Opendatasoft support.")
    )
  }
}
```
  
```{r example-is_available}
page_slug <- "testthat-odsrmd" 
page_elements <- get_ods_page(page_slug) 

is_available("EN", page_elements)
```
  
```{r tests-is_available}
page_slug <- "testthat-odsrmd" 
page_elements <- get_ods_page(page_slug)

test_that("is_available works", {
  expect_true(inherits(is_available, "function"))
  expect_error(is_available("randomword", page_elements))
  expect_silent(is_available("EN", page_elements))
})
```
  



## create_json

Now we combine information coming from the Opendatasoft page (with get_ods_page()) and the Rmarkdown document (with get_body_and_style()) into a JSON object ready to be sent back to the Opendatasoft platform.     

    
```{r function-create_json}
#' Create JSON element to send to ODS platform.   
#' 
#' Combine information coming from the Opendatasoft page (with get_ods_page()) and the Rmarkdown document (with get_body_and_style()) into a JSON object ready to be sent back to the Opendatasoft platform.
#' 
#' @param page_elements List object from get_page(). Contains the title, description, template, language, content, tags and level of restriction of the page. By default in create_json(), if no value is provided to title, description, tags and restricted, create_json() takes the values available in page_elements.    
#' @param body_and_style List object containing body and style of knitted Rmd document coming from get_body_and_style().     
#' @param title A character string specifying the title of the page. If not null, overwrites title from page_elements. 
#' @param description A character string containing the description of the page. If not null, overwrites description from page_elements. 
#' @param chosen_languages A character vector of languages in which the page should be updated. Default to "all", meaning all languages available on the platform. 
#' @param tags A list object of character strings containing the tags describing the page. If not null, overwrites tags from page_elements. 
#' @param restricted A logical TRUE/FALSE indicating the reading status of the page. TRUE will make the page "public" whereas FALSE will keep its access restricted to users who where granted the permission. If not null, overwrites reading status from page_elements.     
#'
#' @return a JSON element  
#' @importFrom jsonlite toJSON
#' @importFrom glue glue_collapse glue
#' @importFrom purrr modify_at
#' 
#' @export
create_json <- function(page_elements, body_and_style,
                        title = NULL, description = NULL,
                        chosen_languages = "all", tags = NULL, restricted = NULL) {

  # type of page_elements : list of length 13 (check names of elements required)
  if (typeof(page_elements) != "list") {
    stop(
      "page_elements must be a list."
    )
  }

  if (length(page_elements) != 13) {
    stop(
      "page_elements must be of length 2."
    )
  }

  if (!"title" %in% names(page_elements) || !"description" %in% names(page_elements) || !"content" %in% names(page_elements) || !"tags" %in% names(page_elements) || !"restricted" %in% names(page_elements)) {
    stop(
      "page_elements must be a named list containing the following elements: title, description, content, tags and restricted."
    )
  }

  # type of body_and_style : list of length 2 (body and style)
  if (typeof(body_and_style) != "list") {
    stop(
      "body_and_style must be a list."
    )
  }

  if (length(body_and_style) != 2) {
    stop(
      "body_and_style must be of length 2."
    )
  }

  if (!identical(names(body_and_style), c("body", "style"))) {
    stop(
      "body_and_style must be a named list with two elements named 'body' and 'style'."
    )
  }

  # type of title : null or character
  if (typeof(title) != "NULL" && typeof(title) != "character") {
    stop(
      "title must be either NULL or character."
    )
  }
  # type of description : null or character
  if (typeof(description) != "NULL" && typeof(description) != "character") {
    stop(
      "description must be either NULL or character."
    )
  }
  # type of chosen_languages : character
  if (typeof(chosen_languages) != "character") {
    stop(
      "chosen_languages must a character string."
    )
  }
  # type of tags : null or character
  if (typeof(tags) != "NULL" && typeof(tags) != "character") {
    stop(
      "tags must be either NULL or character."
    )
  }
  # type of restricted : null or logical
  if (typeof(restricted) != "NULL" && typeof(restricted) != "logical") {
    stop(
      "restricted must be either NULL or logical."
    )
  }

  if (length(chosen_languages) != 1 || chosen_languages != "all") {
    for (l in chosen_languages) {
      is_available(l, page_elements)
    }
  }

  available_languages <- get_languages(page_elements)
  chosen_languages_list <- glue_collapse(chosen_languages, sep = ", ") %>% toupper()
  message(glue("Chosen languages: {chosen_languages_list}."))

  language_list <- Map(function(x) NULL, available_languages)

  JSONlist <- list(
    title = language_list,
    description = NULL,
    template = page_elements$template,
    content = list(
      "html" = language_list,
      "css" = language_list
    ),
    tags = NULL,
    restricted = NULL
  )


  if (length(chosen_languages) == 1 && chosen_languages == "all") {
    language <- available_languages # modify content for all languages
    ignored_languages <- NULL
  } else {
    language <- tolower(chosen_languages) # modify content for some languages, others keep page_elements
    ignored_languages <- setdiff(available_languages, chosen_languages)
  }


  # Add title
  if (is.null(title)) { # no change of title
    if (length(page_elements$title) != 0) { # Some titles exist on the platform, but not necessarily for all languages
      for (l in available_languages) {
        if (!is.null(page_elements$title[[l]])) {
          JSONlist$title <- modify_at(JSONlist$title, .at = l, ~ page_elements$title[[l]])
        } else {
          JSONlist$title <- modify_at(JSONlist$title, .at = l, ~"")
        }
      }
    } else { # No title on the platform and no title defined by the user
      JSONlist$title <- modify_at(JSONlist$title, .at = available_languages, ~"")
    }
  } else { # change of title for chosen languages
    JSONlist$title <- modify_at(JSONlist$title, .at = language, ~title)
    # other languages inherit from page_elements
    for (l in ignored_languages) {
      if (!is.null(page_elements$title[[l]])) {
        JSONlist$title <- modify_at(JSONlist$title, .at = l, ~ page_elements$title[[l]])
      } else {
        JSONlist$title <- modify_at(JSONlist$title, .at = l, ~"")
      }
    }
  }


  # Add description
  if (is.null(description)) {
    JSONlist$description <- page_elements$description
  } else {
    JSONlist$description <- description
  }


  # Add content
  JSONlist$content$html <- modify_at(JSONlist$content$html, .at = language, ~ body_and_style$body)
  for (l in ignored_languages) {
    JSONlist$content$html <- modify_at(JSONlist$content$html, .at = l, ~ page_elements$content$html[[l]])
  }

  JSONlist$content$css <- modify_at(JSONlist$content$css, .at = language, ~ body_and_style$style)
  for (l in ignored_languages) {
    JSONlist$content$css <- modify_at(JSONlist$content$css, .at = l, ~ page_elements$content$css[[l]])
  }

  
  # Add tags
  if (is.null(tags)) {
    JSONlist$tags <- page_elements$tags
  } else {
    JSONlist$tags <- tags
  }

  
  # Add restricted
  if (is.null(restricted)) {
    JSONlist$restricted <- page_elements$restricted
  } else {
    JSONlist$restricted <- restricted
  }

  toJSON(JSONlist, auto_unbox = TRUE)
}

```
  
```{r example-create_json}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to = dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")
page_slug <- "testthat-odsrmd"


body_and_style <- get_body_and_style(path)

page_elements <- get_ods_page(page_slug)

json_to_send <- create_json(page_elements, body_and_style,
  chosen_languages = "all",
  title = NULL, description = NULL,
  tags = NULL, restricted = NULL
)
```
  
```{r tests-create_json}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to = dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")
page_slug <- "testthat-odsrmd"


body_and_style <- get_body_and_style(path)

page_elements <- get_ods_page(page_slug)

json_to_send <- create_json(page_elements, body_and_style,
  chosen_languages = "all",
  title = NULL, description = NULL, 
  tags = NULL, restricted = NULL
)

test_that("create_json works", {
  expect_true(inherits(create_json, "function"))
  expect_type(json_to_send, "character")
  expect_is(json_to_send, "json")
  expect_error(create_json(page_elements, body_and_style,
    chosen_languages = "",
    title = NULL, description = NULL, 
    tags = NULL, restricted = NULL
  ))
  expect_message(create_json(page_elements, body_and_style,
    chosen_languages = "all",
    title = NULL, description = NULL, 
    tags = NULL, restricted = NULL
  ))
})
```


  
## put_ods_page


put_ods_page() updates the content of the page on the Opendatasoft platform with a JSON object. It sends back an HTTP response if the request is successful, otherwise it throws an error.    
    
```{r function-put_ods_page}
#' Put ODS page
#' 
#' Send JSON element to a page from an Opendatasoft platform.  
#' 
#' @param page_slug  Slug of the page (in the backoffice of the platform -> Pages -> New or existing page -> Properties -> Page URL).    
#' @param json_to_send JSON object containing page information, such as title, description, content and tags, that put_ods_page() sends on the page corresponding to the page slug.     
#' @importFrom httr2 request req_auth_basic req_url_path_append req_user_agent req_method req_body_raw req_error req_perform req_options
#'
#' @return If request is successful (i.e. the request was successfully performed and a response with HTTP status code <400 was received), an HTTP response; otherwise it throws an error. 
#' 
#' @export
put_ods_page <- function(page_slug, json_to_send) {
  if (page_slug == "") {
    stop(
      "Please provide a valid page slug."
    )
  }

  if (class(json_to_send) != "json") {
    stop(
      "json_to_send must be of class 'json'."
    )
  }

  ods_domain_id <- Sys.getenv("ODS_DOMAIN_ID")
  ods_username <- Sys.getenv("ODS_USERNAME")
  ods_password <- Sys.getenv("ODS_PASSWORD")

  if (ods_domain_id == "") {
    stop(
      "The domain identifier of the Opendatasoft platform is missing.\n",
      "Please add the environmental variable ODS_DOMAIN_ID to your .Renviron file with the corresponding domain identifier.\n",
      "Reminder, your domain identifier is part of your domain URL : https://your_domain_ID.opendatasoft.com/"
    )
  }

  if (ods_username == "") {
    stop(
      "Your username is missing.\n",
      "Please add the environmental variable ODS_USERNAME to your .Renviron file with the corresponding username.\n"
    )
  }

  if (ods_password == "") {
    stop(
      "Your password is missing.\n",
      "Please add the environmental variable ODS_PASSWORD to your .Renviron file with the corresponding password\n"
    )
  }


  domain_url <- paste0("https://", ods_domain_id, ".opendatasoft.com/api/management/v2/")

  resp <- request(domain_url) %>%
    req_auth_basic(username = ods_username, password = ods_password) %>%
    req_url_path_append("pages", page_slug) %>%
    req_user_agent("R package odsrmd") %>%
    req_method("PUT") %>%
    req_body_raw(json_to_send) %>%
    req_error(body = api_error_body) %>%
    req_perform()

  resp
}

```
  
```{r example-put_ods_page}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to=dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")
page_slug <- "testthat-odsrmd"


body_and_style <- get_body_and_style(path)


page_elements <- get_ods_page(page_slug)

json_to_send <- create_json(page_elements, body_and_style, chosen_languages = c("en", "fr"), 
                        title = "English title", description = NULL,  
                        tags = NULL, restricted = NULL)

put_ods_page(page_slug, json_to_send)


```
  
```{r tests-put_ods_page}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to=dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")
page_slug <- "testthat-odsrmd"


body_and_style <- get_body_and_style(path)

page_elements <- get_ods_page(page_slug)

json_to_send <- create_json(page_elements, body_and_style, chosen_languages = "all", 
                        title = NULL, description = NULL,  
                        tags = NULL, restricted = NULL)

resp <- put_ods_page(page_slug, json_to_send)

test_that("put_ods_page works", {
  expect_true(inherits(put_ods_page, "function")) 
  expect_equal(resp$status, 200)
})

```
  
## update_ods_page
    
```{r function-update_ods_page}
#' Update an ODS page with the content of an Rmd file
#' 
#' All-in-one function to fill in and update an ODS page with the content of an Rmarkdown file. 
#' 
#' @inheritParams get_body_and_style
#' @inheritParams get_ods_page
#' @inheritParams create_json
#' @inheritParams put_ods_page
#'
#' @return If request is successful (i.e. the request was successfully performed and a response with HTTP status code <400 was received), an HTTP response; otherwise it throws an error. 
#' 
#' @export
update_ods_page <- function(path, page_slug, chosen_languages = "all", title = NULL,
                            description = NULL, tags = NULL, restricted = NULL){

body_and_style <- get_body_and_style(path)

page_elements <- get_ods_page(page_slug)

json_to_send <- create_json(page_elements, body_and_style, chosen_languages = chosen_languages, 
                        title, description, tags, restricted)

put_ods_page(page_slug, json_to_send)
}
```
  
```{r example-update_ods_page}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to = dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")
page_slug <- "testthat-odsrmd"

update_ods_page(path, page_slug, chosen_languages = "all", title = NULL,
  description = NULL, tags = NULL, restricted = NULL
)
```
  
```{r tests-update_ods_page}
# Temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)

file.copy(from = system.file("examples/example_rmd.Rmd", package = "odsrmd"), to = dir_tmp)
# browseURL(dir_tmp)
path <- paste0(dir_tmp, "/example_rmd.Rmd")
page_slug <- "testthat-odsrmd"

resp <- update_ods_page(path, page_slug, chosen_languages = "all", title = NULL,
  description = NULL, tags = NULL, restricted = NULL
)


test_that("update_ods_page works", {
  expect_true(inherits(update_ods_page, "function")) 
  expect_equal(resp$status, 200)
    expect_error(update_ods_page(path, page_slug, chosen_languages = "", title = NULL,
  description = NULL, tags = NULL, restricted = NULL
))
  expect_message(update_ods_page(path, page_slug, chosen_languages = "all", title = NULL,
  description = NULL, tags = NULL, restricted = NULL
))
})
```
  


```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started")
```


